Meta-analysis

### 2020-02-17 05_MetaAnalysis.Rmd
Input code from emersons explore markdown

>>>>

```{r netgraphGW}
netgraph(net_con, 
         plastic = FALSE,
         col = "orange",
         thickness =  "number.of.studies",
         points = FALSE, 
         col.points = "black", 
         cex.points = 1,
         number.of.studies = TRUE,
         cex.number.of.studies = 1,
         col.number.of.studies = "black",
         bg.number.of.studies = "orange",
         multiarm = FALSE,
         col.multiarm = "lightblue",
         pos.number.of.studies = 0.5)
```

```{r}
netleague(net_con)
```

```{r}
decomp.design(net_con)
```

```{r}
netsplit(net_con)
```
```{r}
nm1 <- netmeasures(net_con)

plot(nm1$meanpath, nm1$minpar, pch="",
     xlab="Mean path length", ylab="Minimal parallelism")
text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex=0.8)
```
